---
title: "Philadelphia Demolition Data"
author: "Jay Fisher"
date: "August 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_packages, include=FALSE}
library(tidyverse)
library(lubridate)
```

```{r read_data, include=FALSE}
# Read in files
li_demolitions <- read_csv("C:/Users/fishe/Desktop/li_demolitions.csv")
```

```{r completed_demos, include=FALSE}
# Completed demos, with completed year and days to complete columns added in
li_demo_complete <- li_demolitions %>%
  filter(status == "COMPLETED", is.na(li_demolitions$completed_date) == F) %>% 
  mutate(year_complete = year(completed_date),
         days_to_complete = (completed_date - start_date)/((60*60)*24),
         zip_simple = str_sub(zip, 1, 5)
           )
```

## Introduction
### Data
- Demolition Data 

### Tools
- RStudio
- R Markdown
- `tidyverse`, `lubridate` R packages

## Total Demolitions per Year
```{r echo=FALSE}
li_demo_complete %>% 
  ggplot(aes(x = year_complete)) +
  geom_bar() +
  theme_bw()
```

<br>

## Average Time to Complete Demolition by Year
```{r avg_time_complete_demo_by_year, echo=FALSE}
li_demo_complete %>%
  group_by(year_complete) %>% 
  summarise(avg_days_to_complete = mean(days_to_complete)) %>% 
  ggplot(aes(x = year_complete, y = as.numeric(avg_days_to_complete))) +
    geom_bar(stat="identity") + 
  ylab("Avg Days To Complete") +
  theme_bw()
```

<br>

## Why is the average time to complete so high in 2013?
```{r 2013_avg_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
li_demo_complete %>% 
  filter(year_complete != c(2007)) %>% 
  ggplot(aes(x = year_complete, y = days_to_complete, group = year_complete)) +
  geom_boxplot() +
  # geom_hline(yintercept = 365, linetype = 2, color = "grey") +
  theme_bw() +
  theme(panel.grid.major.y = element_line(linetype = 2),
        panel.grid.minor.y = element_blank()) +
  scale_y_continuous(breaks = seq(0, (365*7), 365))
```
<br>
Guesses: Higher number of multi-year demolition projects finished, larger property sizes

<br>

## Zip Codes With Most Demolitions in 2017
```{r zips_with_most_demos_in_2017, echo=FALSE, message=FALSE, warning=FALSE}
# 2017: 19121, 19132, 19143, 19146, 19125
demo_top_5_2017 <- li_demo_complete %>% 
  filter(year_complete != 2018, 
         zip_simple == "19121" | zip_simple == "19132" | zip_simple == "19143" | zip_simple == '19146' | zip_simple == '19125') %>% 
  group_by(zip_simple, year_complete) %>% 
  summarise(count = n())

demo_top_5_2017 %>% 
  ggplot(aes(x = year_complete, y = count, group = zip_simple, color = zip_simple)) +
    geom_line(size = 2, alpha = 0.75) +
  theme_bw() +
  scale_x_continuous(breaks=seq(2007, 2017, 1)) +
  theme(legend.title=element_blank(),
        legend.direction = "horizontal", legend.position = "bottom")
```

The Top 5 zip codes with demolitions in 2017 are 19121, 19132, 19143, 19146, and 19125.

19121 and 19132 are North Philadelphia neighboorhoods. 19146 is South Philly (Point Breeze). 19143 - West Philly. 19125 - Fishtown.

<hr>

## Data Quality Issues
```{r include=FALSE}
status_complete_no_completed_date <- li_demolitions %>%
  filter(status == "COMPLETED", is.na(li_demolitions$completed_date))
```

- Where status = COMPLETED, but data set does not have completed_date: `r nrow(status_complete_no_completed_date)`
- Two examples where Completed Date happened before Start Date


